The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-23 paper/ms.tex
minor update in the conclusions

\section{Conclusions}
\label{sec:conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Ly$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.

>>>>

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have estimated the effects of gas bulk rotation on
the morphology of the Lyman $\alpha$ line in galaxies. The results are
based on the study of a set of simplified configuration of an
homogeneous sphere rotating as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Ly$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.
